To boldly go where no science...

### 2016-05-03 nyu-data-science-reproducibility-16/be-bold.Rmd
add Databrary leaf

- Behavior rich, complex
- Numeric, text-based measures reduce that complexity
- **Video captures and preserves it**

@@

>>>>

- Behavior rich, complex
- Numeric, text-based measures reduce that complexity
- **Video captures and preserves it

@@

<iframe src="https://databrary.org/about/jobs.html" width=640px height=400px>
</iframe>

<div class="centered">
<img src="img/databrary-leaf-large.png" height=450>

<http://github.com/databrary/presentations/nyu-data-science-reproducibility-16/>
</div>
